\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-09-15 submission/manuscript.Rmd
Added metagenomes ENA accession.

Obtained sequences were analyzed on a Life Science Compute Cluster (LiSC) (CUBE -- Computational Systems Biology, University of Vienna). Individual sequences were assembled using MEGAHIT (version  1.1.2) [@Li2015] under default settings. Putative genes were predicted from contings longer than 200 bp using Prodigal (version  2.6.3) [@Hyatt2010] in metagenome mode (-p meta). Abundances of predicted genes were expressed as Reads Per Kilobase Million (RPKM) and calculated using the BWA algorithm (version  0.7.16a) [@Li2009a]. All predicted genes were functionally annotated using the eggNOG-mapper [@Huerta-Cepas2017] and eggNOG database (version 5.0) [@Huerta-Cepas2019]. Sequence taxonomy classification was determined using the lowest common ancestor algorithm adapted from DIAMOND (version 0.8.36) [@Buchfink2015] and by searching against the NCBI non-redundant database (NR). To determine phylogeny the top 10 \si{\percent} hits with an e-value < 1 × 10^-5^ were used (\-\-top 10). Sequence renaming, coverage information computing and metagenomic statistics calculations were performed using software tools from BBTools (https://jgi.doe.gov/data-and-tools/bbtools). Metagenomic sequences obtained in this study have been deposited in the European Nucleotide Archive (ENA) at EMBL-EBI under accession numbers **TO BE ADDED**.

>>>>

Obtained sequences were analyzed on a Life Science Compute Cluster (LiSC) (CUBE -- Computational Systems Biology, University of Vienna). Individual sequences were assembled using MEGAHIT (version  1.1.2) [@Li2015] under default settings. Putative genes were predicted from contings longer than 200 bp using Prodigal (version  2.6.3) [@Hyatt2010] in metagenome mode (-p meta). Abundances of predicted genes were expressed as Reads Per Kilobase Million (RPKM) and calculated using the BWA algorithm (version  0.7.16a) [@Li2009a]. All predicted genes were functionally annotated using the eggNOG-mapper [@Huerta-Cepas2017] and eggNOG database (version 5.0) [@Huerta-Cepas2019]. Sequence taxonomy classification was determined using the lowest common ancestor algorithm adapted from DIAMOND (version 0.8.36) [@Buchfink2015] and by searching against the NCBI non-redundant database (NR). To determine phylogeny the top 10 \si{\percent} hits with an e-value < 1 × 10^-5^ were used (\-\-top 10). Sequence renaming, coverage information computing and metagenomic statistics calculations were performed using software tools from BBTools (https://jgi.doe.gov/data-and-tools/bbtools). Metagenomic sequences obtained in this study have been deposited in the European Nucleotide Archive (ENA) at EMBL-EBI under accession numbers SAMEA6648795, SAMEA6648797, SAMEA6648809 and SAMEA6648811.

### 2020-09-15 submission/manuscript.tex
Added metagenomes ENA accession.

Obtained sequences were analyzed on a Life Science Compute Cluster
(LiSC) (CUBE -- Computational Systems Biology, University of Vienna).
Individual sequences were assembled using MEGAHIT (version 1.1.2) (Li
\emph{et al.}, 2015) under default settings. Putative genes were
predicted from contings longer than 200 bp using Prodigal (version
2.6.3) (Hyatt \emph{et al.}, 2010) in metagenome mode (-p meta).
Abundances of predicted genes were expressed as Reads Per Kilobase
Million (RPKM) and calculated using the BWA algorithm (version 0.7.16a)
(Li and Durbin, 2009). All predicted genes were functionally annotated
using the eggNOG-mapper (Huerta-Cepas \emph{et al.}, 2017) and eggNOG
database (version 5.0) (Huerta-Cepas \emph{et al.}, 2019). Sequence
taxonomy classification was determined using the lowest common ancestor
algorithm adapted from DIAMOND (version 0.8.36) (Buchfink \emph{et al.},
2015) and by searching against the NCBI non-redundant database (NR). To
determine phylogeny the top 10 \si{\percent} hits with an e-value
\textless{} 1 × 10\textsuperscript{-5} were used (-\/-top 10). Sequence
renaming, coverage information computing and metagenomic statistics
calculations were performed using software tools from BBTools
(\url{https://jgi.doe.gov/data-and-tools/bbtools}). Metagenomic
sequences obtained in this study have been deposited in the European
Nucleotide Archive (ENA) at EMBL-EBI under accession numbers \textbf{TO
BE ADDED}.

>>>>

Obtained sequences were analyzed on a Life Science Compute Cluster
(LiSC) (CUBE -- Computational Systems Biology, University of Vienna).
Individual sequences were assembled using MEGAHIT (version 1.1.2) (Li
\emph{et al.}, 2015) under default settings. Putative genes were
predicted from contings longer than 200 bp using Prodigal (version
2.6.3) (Hyatt \emph{et al.}, 2010) in metagenome mode (-p meta).
Abundances of predicted genes were expressed as Reads Per Kilobase
Million (RPKM) and calculated using the BWA algorithm (version 0.7.16a)
(Li and Durbin, 2009). All predicted genes were functionally annotated
using the eggNOG-mapper (Huerta-Cepas \emph{et al.}, 2017) and eggNOG
database (version 5.0) (Huerta-Cepas \emph{et al.}, 2019). Sequence
taxonomy classification was determined using the lowest common ancestor
algorithm adapted from DIAMOND (version 0.8.36) (Buchfink \emph{et al.},
2015) and by searching against the NCBI non-redundant database (NR). To
determine phylogeny the top 10 \si{\percent} hits with an e-value
\textless{} 1 × 10\textsuperscript{-5} were used (-\/-top 10). Sequence
renaming, coverage information computing and metagenomic statistics
calculations were performed using software tools from BBTools
(\url{https://jgi.doe.gov/data-and-tools/bbtools}). Metagenomic
sequences obtained in this study have been deposited in the European
Nucleotide Archive (ENA) at EMBL-EBI under accession numbers
SAMEA6648795, SAMEA6648797, SAMEA6648809 and SAMEA6648811.
